### 2014-03-28 ms_probaweb.tex
Added two alternative titles
Updated the biblatex command styles, and a bunch of edits in the intro

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{color,lineno,setspace,multirow,kpfonts}
\usepackage{graphicx}
\usepackage[top=2.4cm,left=2.4cm,top=2.4cm,bottom=2.4cm,includefoot]{geometry}
\usepackage[style=bes]{biblatex}
\usepackage{rotating}

\bibliography{library, tim}

@@

\textbf{Title:} A quantitative framework for network biogeography\\
% Alternative: The distribution of ecological interactions

\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Timoth\'ee Poisot$^{1,2,3}$, Neo
Martinez$^{4}$, Jennifer Dunne$^{5}$, Jason Tylianakis$^{3}$, Nicolas
Mouquet$^{6}$, Daniel Stouffer$^{3}$ \\

1: Canada Research Chair in Biogeography and community ecology. D\'epartement de
biologie, chimie et g\'eographique, Universit\'e du Qu\'ebec \`a Rimouski, 300
All\'ee des Ursulines, Qu\'ebec, Canada. G5L 3A1.\\

@@

Most ecology textbooks define the ecological community at \quote{the pool of
species occupying a given location at a given time, and the list of their
interactions} (ref to Morin?). Yet we oft forget the last part of this
definition, focusing on species and neglecting the way they interact.

@@

\newpage
%========================================================%
\section*{A probabilistic representation of ecological networks}

Interaction networks do vary in space and time because any given pairwise
interaction could either occur or not at any particular location. We seek to
represent the probability an interaction between species $i$ and $j$ occurs at
location $y$. We consequently define $L_{ijy}$ as a stochastic variable taking a
value of 1 when an interaction occurs and are thus looking at the probabilty of
this event, $P(L_{ijy})$. There are several factors that could impact the
occurrence of an interaction and we will describe them below. But ultimately,
this probability depends on the spatial and temporal scale of observation. As
long as the interaction probability is not null, the probability of observing an
interaction will tend to 1 as the scale of observation increases.

The occurrence of an interaction requires the co-occurrence of species
$i$ and $j$. This argument might seem trivial at first, but the explicit
consideration of this condition in the probabilistic representation of
ecological networks will prove fundamental to understand their variation. We
thus define $X_{iy}$ as a stochastic variable representing the occurrence of a
species $i$ at location $y$, and similarly $X_{ijy}$ the co-occurrence of species
$i$ and $j$. The quantity we seek to understand is the probability of a joint
event:

@@

\subsection*{Species \& link distribution models}

@@

\newpage
%========================================================%
\section*{Acknowledgements}
This is tis a contribution to the Santa Fe Institute working group \emph{Networks over
ecological gradients}. DG received financial support from NSERC and Canada
Research Chair program. TP is supported by a MELS-FQRNT post-doctoral
fellowship. DG, TP, and DBS received financial support from the CIEE.
\newpage

>>>>

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{color,lineno,setspace,multirow,kpfonts}
\usepackage{graphicx}
\usepackage[top=2.4cm,left=2.4cm,top=2.4cm,bottom=2.4cm,includefoot]{geometry}
\usepackage[style=bes, backend=bibtex]{biblatex}
\usepackage{rotating}

\addbibresource{tim.bib}

@@

\textbf{Title:} A quantitative framework for network biogeography\\
% Alternative: The distribution of ecological interactions 
% Alternative: The biogeography of ecological interactions
% Alternative: Community (macro)ecology: integrating species interactions and species distributions

\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Timoth\'ee Poisot$^{1,2,3}$, N\'eo
Martinez$^{4}$, Jennifer A. Dunne$^{5}$, Jason Tylianakis$^{3}$, Nicolas
Mouquet$^{6}$, Daniel B. Stouffer$^{3}$ \\

1: Canada Research Chair in Biogeography and community ecology. D\'epartement de
biologie, chimie et g\'eographie, Universit\'e du Qu\'ebec \`a Rimouski, 300
All\'ee des Ursulines, Qu\'ebec, Canada. G5L 3A1.\\

@@

Ecology textbooks define the structure of an ecological community as
\emph{the pool of species occupying a given location at a given time, and
the way these species interact} (ref to Morin?). It is therefore surprizing
that ecological research on the variation of community structure has focused
on species turnover (refs), almost entirely neglecting variation in the way
species interact (refs).

@@

\newpage
%========================================================%
\section*{A probabilistic representation of ecological interactions networks}

%% We need to be careful: ecological network / interaction network / etc.
%% I vote interaction networks, ecological network can be a spatial graph.
%% Also, since we're going to say "interaction" a lot, interaction network
%% makes sense. -- tp

Networks of species interactions vary in space and time because any given
pairwise interaction could either occur or not at any particular location.
Understanding this variation amounts to be able to determine the probability
that two species ($i$ and $j$) will interact at a given time/location ($y$);
the existence of an interaction in this situation is thus essentially a
stochastic variable, which we note $L_{ij,y}$. It takes a value of 1 where the
interaction occurs, and 0 elsewhere. We note $P(L_{ij,y})$ the probability
of this event. There are several factors that could impact the occurrence
of an interaction and we will describe them below. But ultimately, this
probability depends on the spatial and temporal scale of observation. As long
as the probability of a particular interaction is not null, the probability
of observing it at least once will become asymptotically closer to 1 when
the scale of observation increases.
% OK I like this paragraph, but we're REALLY NOT talking about factors or mechanisms here.
% This whole framework is top-down/inferential, so we should at least have a paragraph in the
% intro essentially summing up our preprint on network variation, and be clear on the
% fact that we don't touch on mechanisms.

The occurrence of an interaction requires the co-occurrence of species $i$ and
$j$. This argument might seem trivial at first, but the explicit consideration
of this condition in the probabilistic representation of ecological networks
will prove fundamental to understand their variation.
% We already make this point in betalink, should we summarize it briefly?
We thus define $X_{iy}$
as a stochastic variable representing the occurrence of a species $i$ at
location $y$, and similarly $X_{ijy}$ the co-occurrence of species $i$ and
$j$. The quantity we seek to understand is the probability of a joint event:

@@

% Do you mean "Patterns-generating models testing"?

\subsection*{Species \& interactions distribution models}

@@

\newpage
%========================================================%
\section*{Acknowledgements}
This is a contribution to the working groups \emph{Networks over ecological
gradients} (Santa Fe Institute) and \emph{Continental-scale variation of
ecological networks}. (Canadian Institute for Ecology and Evolution). DG
received financial support from NSERC and Canada Research Chair program. TP
is supported by a MELS-FQRNT post-doctoral fellowship.
\newpage
